Incentivizing Exploration with Unbiased History

### 2018-11-01 2level.tex
Fixed a typo.

\begin{assumption}\label{ass:simplifying}
In each round $t$, the estimates $\hat{\mu}_{t,a}$ depend only the multiset 
    $\left\{\; (a_s,r_s):\;s\in S_t \;\right\}$,
called \emph{anonymized subhistory}. Each agent forms its estimates according to the same \emph{estimate function}: a function $f$ from subhistories to $[0,1]^K$, so that the estimate vector
        $(\hat{\mu}_{t,a}:\, a\in\A)$
equals $f(m_t)$. 
\end{assumption}

>>>>

\begin{assumption}\label{ass:simplifying}
In each round $t$, the estimates $\hat{\mu}_{t,a}$ depend only on the multiset 
    $\left\{\; (a_s,r_s):\;s\in S_t \;\right\}$,
called \emph{anonymized subhistory}. Each agent forms its estimates according to the same \emph{estimate function}: a function $f$ from subhistories to $[0,1]^K$, so that the estimate vector
        $(\hat{\mu}_{t,a}:\, a\in\A)$
equals $f(m_t)$. 
\end{assumption}
